Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
caption Fig 2

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
\node (histlabel1) at (2.5, 0.01) {$\mathbf{S}\boldsymbol{x}$};
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
\node at (1, -0.35) {(a)};
\node (histlabel2) at (7.8, 0.01) {$\log \mathbf{S}\boldsymbol{x}$};
\node[anchor=south west,inner sep=0] at (3.3, 0) {\includegraphics[height=2cm,width=3.5cm]{feature_histogram_logcompressed.png}};
\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
\draw[-{Latex[length=2mm]}] (5, 0.01) -- (5, 2.5);
\node at (5.5, -0.35) {(b)};
\end{tikzpicture}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
\node (histlabel1) at (2.3, 0.01) {$\mathbf{S}\boldsymbol{x}(\gamma)$};
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
\node at (0.8, -0.35) {(a)};
\node (histlabel2) at (7.6, 0.01) {$\log \mathbf{S}\boldsymbol{x}(\gamma)$};
\node[anchor=south west,inner sep=0] at (3.45, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
\draw[-{Latex[length=2mm]}] (4.9, 0.01) -- (4.9, 2.5);
\node at (4.9, -0.35) {(b)};
\end{tikzpicture}
\caption{
\label{fig:histograms}
Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
(a) before and (b) after logarithmic compression.}
\end{center}
\end{figure}
